% \subsection{Notes}
% \begin{enumerate}
%     \item Motivate The Problem Cosmo
%     \item Introduce The Theory Cosmo + Lensing
%     \item Explain How Theory Solves The Problem
%     \item Current Results/ Experiments
%     \item Explain Problems with WeakLensing
%     \item Summarise
% \end{enumerate}

% Discuss probing the large scale universe with CMB, supernvae, clustering
% and lensing. 
% Note weak lensing makes no assumptions about the nature of dark matter
% and no assumptions about relationship between visible matter and mass therefore
% it provides a directly measured mass distribution in the universe as a function of 
% redshift. Therefore we can get info on DE and DM directly. It is sensitive to intial
% conditions so it can even give info on inflation. 
\subsection{Standard Model of Cosmology}
\begin{enumerate}
    \item Motivation (modified gravity vs Dark energy) is DE constant in space ? and time ?
    \item FRW Standard Cosmology 
    \item Distance Measures In Cosmo
    \item Gravitational Evolution of Dark matter
    \item Observables and Parameters
\end{enumerate}
The fundamental assumption in cosmology, known as the cosmological principle, is that we live in a homogenous and isotropic universe \cite{general_2013}. 
Remeber to show the Standard Model parameters! can be found in wikipedia.
\par Angular diameter distance is the one of relvance in lensing (distance measures in cosmology)
Distances in cosmo \cite{Hogg:1999ad}
lol 

\par For current and future surveys, one goal is to use the redshifts of the background galaxies (often approximated using photometric redshifts) to divide the survey into multiple redshift bins. The low-redshift bins will only be lensed by structures very near to us, while the high-redshift bins will be lensed by structures over a wide range of redshift. This technique, dubbed "cosmic tomography", makes it possible to map out the 3D distribution of mass. Because the third dimension involves not only distance but cosmic time, tomographic weak lensing is sensitive not only to the matter power spectrum today, but also to its evolution over the history of the universe, and the expansion history of the universe during that time. This is a much more valuable cosmological probe, and many proposed experiments to measure the properties of dark energy and dark matter have focused on weak lensing, such as the Dark Energy Survey, Pan-STARRS, and Large Synoptic Survey Telescope. 

\subsubsection{Matter Power Spectrum}
\cite{extragalactic}

\subsection{Bending of Light}
The fundamental concept on which weak lensing is built is gravity's ability to alter the path of a photon.
In this section we review the theory behind the bending of light necessary to develop the weak lensing formalism.
\subsubsection{Newtonian Lens}
\label{subsec:newtonlens}

It is a common misconception that the gravitational bending of light is an exclusive property of GR.
However, gravity induced alterations to a photon's path are predicted by newtonian mechanics \cite{lensingbook}. To illustrate this 
consider a mass $M$ located at the origin of the cartesian plane and a corpuscle(newtonian photon) 
propagating along the $x=b$ line (in this context $b$ is known as the impact parameter). 
Newton's second law predicts that the presence of the point mass will result in a momentum transfer
between the two objects. If the corpuscle starts with 
momentum $(p,0)$ then it will end up with momentum $(p_x,p_y)$.
Therefore, the particle path is deflected by some angle $\Delta \theta$. The deflection angle is 
simply given by 

\begin{equation}
  \sin(\Delta \theta) = \frac{p_y}{\sqrt{p_x^2+p_y^2}}
  \label{deflectionnewton}
\end{equation}


\par For very small deflections we have $p\approx p_x >> p_y$ and $\Delta \theta << 1$. 
Therefore \autoref{deflectionnewton} simplifies to $\Delta \theta
\approx \frac{p_y}{p_x}$. We now consider the infinitesimal deflection along the entire path of the photon with
$d\Delta \theta = \frac{dp_y}{p_x} = \frac{1}{px} dx \frac{dp_y}{dx}$. Therefore, we can find the deflection
angle by 

\begin{equation}
  \begin{split}
  \Delta \theta_N &= -\frac{1}{p_x} \int dx \frac{dp_y}{dx} \\
  &= -\frac{1}{cp_x} \int dx \frac{dp_y}{dt} = -\frac{1}{cp_x} \int F_y dx \\ 
  &= \frac{2GM}{c^2b}
  \end{split}  
  \label{newtonbend}
\end{equation}

We note that the mass of the corpuscle cancels out of the deflection equation. Therefore this equation applies
for massless particles i.e. photons. Therefore \autoref{newtonbend} provides a newtonian description for the 
bending of light \cite{lensingbook}.

\subsubsection{General Relativistic Bending of Light}
In this subsubsection I give a quick sketch of the bending of light in the context of general relativity,
for a more detailed calculation please consult \cite{GR1}.

\par The Einstein's field equations in the presence of a charge free static point mass is uniquely solved by 
the Schwarzchild metric \cite{GR1}. The Schwarzchild metric is

\begin{equation}
  ds^2 = \left ( 1-\frac{r_s}{r} \right )  dt^2 - \left( 1-\frac{r_s}{r}\right) ^{-1} dr^2 -r^2 d\Omega^2
  \label{schwarz}
\end{equation}

Where $r_s$ is the Shcwarzchild radius of the system given by $r_s=2 \mu = 2GM/c^2$. We can analyze the path of the photon from \autoref{subsec:newtonlens} by studying the geodesic equations of the metric and finding the conserved
quantities of the system. We can then combine the conservation equations with the tangent vector norm condition for a 
null path to get the shape equation of the system as 

\begin{equation}
  \frac{d\phi}{dr} = \frac{1}{r^2} \left(\frac{1}{b^2}- \frac{1}{r^2} \left(1-\frac{2\mu}{r}\right) \right)^{-1/2}
  \label{shapeeqbend}
\end{equation}

where $(r,\phi)$ are the photons position in 2D polar coordinates and $b$ is the impact parameter. Rewriting this equation
under the transformation of $r = 1/u$ and working pertrubatively around $u(\mu =0) = \frac{1}{b}\sin \phi
$ we get 

\begin{equation}
  u(\phi) \approx \frac{1}{b}\sin \phi + \frac{3\mu}{2b^2} \left(1+\frac{1}{3}\cos 2 \phi \right)
  \label{eq:pertshape}
\end{equation}

in the limit were $\phi << 1$ and $u \rightarrow 0$ \autoref{eq:pertshape} simplifies to $\phi = \Delta \theta_N =\frac{2GM}{c^2b} $. Geometrically the deflection is given by $\Delta \theta = 2\phi$ and therefore the deflection angle is

\begin{equation}
  \Delta \theta = 2\Delta \theta_N=\frac{4GM}{c^2b}
  \label{grbend}
\end{equation}

We conclude that general relativity predicts a factor of 2 greater deflection form a point mass than is predicted by newtonian mechanics. This relationship greatly simplifies the formalism developed for weak lensing. 

\subsection{Weak Lensing Formalism}
Now that we have a theoratical understanding of the Cosmological parameters we would like to measure as well as an understanding of how gravitational fields impact the path of light we are ready to develop the weak lensing formalism on which all weak lensing applications are built.
Talk about thin lens and how the formalism revloves around projecting newtonian potential onto the lens 2D surface.\cite{basicLens}
